---
title: "Advanced Visualization Techniques"
subtitle: "Statistical Computing & Programming"
author: "Shawn Santo"
institute: ""
date: ""
output:
  xaringan::moon_reader:
    css: "slides.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Supplementary materials

Full video lecture available in Zoom Cloud Recordings

Additional resources

- [Extend ggplot2](https://ggplot2.tidyverse.org/articles/extending-ggplot2.html) 
  by creating your own stat, geom, and theme
- [Network visualization with `ggraph`](https://ggraph.data-imaginist.com)
- [Plotly ggplot2 library](https://plotly.com/ggplot2/)
- [Template themes with `ggthemes`](https://github.com/jrnold/ggthemes)

---

## Packages

For these slides we will use the following packages.

.normal[
```{r}
library(tidyverse)
library(gapminder)  # some data
library(ggpol)      # parliament plots and more
library(patchwork)  # combining plots
library(gganimate)  # animations
library(ggiraph)    # interactive plots
```
]

Install any CRAN packages you do not have with 
`install.packages("package_name")`.

<br><br><br><br>

**Code not shown for plots is available in the presentation notes. Press `P`.**

---

class: inverse, center, middle

# Annotate plots

---

## Annotation

`annotate()` allows you to add additional geoms to your plot space. Because
the corresponding geom is not mapped to variables of a data frame, it is
very convenient for adding text or highlighting a point.

You can use a single `annotate()` call or many.

```{r eval=FALSE}
ggplot() +
  annotate(geom = "text", x = 10, y = 10, 
           label = "Text at (10, 10)", size = 10) +
  annotate(geom = "point", x = 20, y = -20, color = "red", size = 4) +
  annotate(geom = "segment", x = 0, xend = 10, y = 0, yend = 0, 
           size = 3, color = "blue") +
  annotate(geom = "curve", x = 10, xend = 15, y = -10, yend = -5, 
           size = 3, color = "green") +
  annotate(geom = "curve", x = 10, xend = 15, y = -5, yend = -10, 
           size = 3, color = "orange")
```

Use the `...` in annotate to pass geom-specific arguments and values.

---

## Annotation

```{r echo=FALSE}
ggplot() +
  annotate(geom = "text", x = 10, y = 10, label = "Text at (10, 10)", size = 10) +
  annotate(geom = "point", x = 20, y = -20, color = "red", size = 4) +
  annotate(geom = "segment", x = 0, xend = 10, y = 0, yend = 0, color = "blue", size = 3) +
  annotate(geom = "curve", x = 10, xend = 15, y = -10, yend = -5, color = "green", size = 3) +
  annotate(geom = "curve", x = 10, xend = 15, y = -5, yend = -10, color = "orange", size = 3) +
  xlim(c(0, 20)) +
  theme_minimal(base_size = 20)
```

---

## Annotate to enhance

Depending on your data, annotations can be a great way to enhance the reader's
visual understanding.

```{r}
url <- str_c("http://www2.stat.duke.edu/~sms185/",
             "data/sports/events.csv")
events <- read_csv(url)
```

Let's only look at the shots that occurred during this match.

```{r}
shots <- events %>% 
  filter(event_name == "Shot") %>% 
  select(team_id, start_x, start_y)
```

---

## Annotate to enhance

.tiny[
```{r fig.width=7, fig.height=4.66}
ggplot(shots, mapping = aes(x = start_x, y = start_y)) +
  geom_point(mapping = aes(color = factor(team_id)), size = 3) +
  labs(color = "Team ID") +
  theme(legend.position = "bottom")
```
]

--

Not very interesting or informative!

--

With a few annotations, we can enhance this a lot.

---

## Annotate to enhance

.tiny[
```{r fig.width=7, fig.height=4.66}
ggplot(shots, mapping = aes(x = start_x, y = start_y)) +
  geom_point(mapping = aes(color = factor(team_id)), size = 3) +
  labs(color = "Team ID") +
  theme_void() +
  theme(legend.position = "bottom")
```
]

--

Setting `theme_void()` doesn't help much either.

---

## Annotate to enhance

Create a function called `fc_annotate_pitch()` that has all the pitch field
markings.

.tiny.pull-left[
```{r eval = FALSE}
  fcn_list <- list(
    boundary          = "annotate",
    center_circle     = "annotate",
                    ⋮
    lower_right_arc   = "annotate",
    upper_right_arc   = "annotate"
  )
```
]

.tiny.pull-right[
```{r eval=FALSE}
arg_list <- list(
    boundary = list(
      geom  = "rect",
      xmin  = x_min,
      xmax  = x_max,
      ymin  = y_min,
      ymax  = y_max,
      color = palette_color,
      fill  = palette_fill,
      size  = 1.5
    ),
            ⋮
    
    upper_right_arc = list(
      geom  = "curve",
      x     = ifelse(coord_flip, x_max, x_max - 2 * x_adj),
      xend  = ifelse(coord_flip, x_max - 2 * x_adj, x_max),
      y     = ifelse(coord_flip, y_max - 2 * y_adj, y_max),
      yend  = ifelse(coord_flip, y_max, y_max - 2 * y_adj),
      color = palette_color
    )
  )
```
]

Combine the functions and their parameters with 
`invoke_map(fcn_list, arg_list)`.

```{r echo=FALSE}
fc_annotate_pitch <- function(dimensions = c(105, 70), palette = "gw",
                              color = NULL, fill = NULL, coord_flip = FALSE) {

  palette_color <- switch(
    palette,
    "gw"      = "grey60",
    "classic" = "white",
    "smurf"   = "white",
    "dark"    = "white",
    "wc"      = "#ffffff",
    "bw"      = "#130a06"
  )

  palette_fill <- switch(
    palette,
    "gw"      = "white",
    "classic" = "#196f0c",
    "smurf"   = "#0033A0",
    "dark"    = "#130a06",
    "wc"      = "#8d1b3d",
    "bw"      = "white"
  )

  if (!is.null(color)) palette_color <- color
  if (!is.null(fill)) palette_fill <- fill

  x_min <- 0
  y_min <- 0
  x_max <- dimensions[1]
  y_max <- dimensions[2]
  x_mid <- (x_max - x_min) / 2
  y_mid <- (y_max - y_min) / 2
  x_adj <- x_max / 105
  y_adj <- y_max / 70

  fcn_list <- list(
    boundary          = "annotate",
    center_circle     = "annotate",
    center_point      = "annotate",
    center_line       = "annotate",
    left_penalty_box  = "annotate",
    right_penalty_box = "annotate",
    left_goal_box     = "annotate",
    right_goal_box    = "annotate",
    left_penalty_dot  = "annotate",
    right_penalty_dot = "annotate",
    left_goal         = "annotate",
    right_goal        = "annotate",
    left_box_arc      = "annotate",
    right_box_arc     = "annotate",
    lower_left_arc    = "annotate",
    upper_left_arc    = "annotate",
    lower_right_arc   = "annotate",
    upper_right_arc   = "annotate"
  )

  arg_list <- list(
    boundary = list(
      geom  = "rect",
      xmin  = x_min,
      xmax  = x_max,
      ymin  = y_min,
      ymax  = y_max,
      color = palette_color,
      fill  = palette_fill,
      size  = 1.5
    ),
    center_circle = list(
      geom  = "path",
      x     = x_mid + (9.15 * x_adj) * cos(seq(0, 2 * pi, length.out = 100)),
      y     = y_mid + (9.15 * y_adj) * sin(seq(0, 2 * pi, length.out = 100)),
      color = palette_color
    ),
    center_point = list(
      geom  = "point",
      x     = x_mid,
      y     = y_mid,
      size  = 2,
      color = palette_color
    ),
    center_line = list(
      geom  = "segment",
      x     = x_mid,
      y     = y_min,
      xend  = x_mid,
      yend  = y_max,
      color = palette_color
    ),
    left_penalty_box = list(
      geom  = "rect",
      xmin  = x_min,
      xmax  = 16.5 * x_adj,
      ymin  = (y_max - (40.3 * y_adj)) / 2,
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (40.3 * y_adj),
      color = palette_color,
      fill  = palette_fill,
      alpha = 0
    ),
    right_penalty_box = list(
      geom  = "rect",
      xmin  = x_max - (16.5 * x_adj),
      xmax  = x_max,
      ymin  = (y_max - (40.3 * y_adj)) / 2,
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (40.3 * y_adj),
      color = palette_color,
      fill  = palette_fill,
      alpha = 0
    ),
    left_goal_box = list(
      geom  = "rect",
      xmin  = 0,
      xmax  = 5.5 * x_adj,
      ymin  = (y_max - (40.3 * y_adj)) / 2 + (11 * y_adj),
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (29.3 * y_adj),
      color = palette_color,
      fill  = palette_fill,
      alpha = 0
    ),
    right_goal_box = list(
      geom  = "rect",
      xmin  = x_max - (5.5 * x_adj),
      xmax  = x_max,
      ymin  = (y_max - (40.3 * y_adj)) / 2 + (11 * y_adj),
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (29.3 * y_adj),
      color = palette_color,
      fill  = palette_fill,
      alpha = 0
    ),
    left_penalty_dot = list(
      geom  = "point",
      x     = 11 * x_adj,
      y     = y_mid,
      size  = 2,
      color = palette_color
    ),
    right_penalty_dot = list(
      geom  = "point",
      x     = x_max - (11 * x_adj),
      y     = y_mid,
      size  = 2,
      color = palette_color
    ),
    left_goal = list(
      geom  = "rect",
      xmin  = x_min - (2.4 * x_adj),
      xmax  = x_min,
      ymin  = (y_max - (40.3 * y_adj)) / 2 + (16.5 * y_adj),
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (23.3 * y_adj),
      color = palette_color,
      fill  = palette_color
    ),
    right_goal = list(
      geom  = "rect",
      xmin  = x_max,
      xmax  = x_max + (2.4 * x_adj),
      ymin  = (y_max - (40.3 * y_adj)) / 2 + (16.5 * y_adj),
      ymax  = (y_max - (40.3 * y_adj)) / 2 + (23.3 * y_adj),
      color = palette_color,
      fill  = palette_color
    ),
    left_box_arc = list(
      geom  = "curve",
      x     = 16.5 * x_adj,
      xend  = 16.5 * x_adj,
      y     = y_mid - (ifelse(coord_flip, -1, 1) *
                         sqrt((y_adj * 5.5) ^ 2 + (y_adj * 9.15) ^ 2)),
      yend  = y_mid + (ifelse(coord_flip, -1, 1) *
                         sqrt((y_adj * 5.5) ^ 2 + (y_adj * 9.15) ^ 2)),
      color = palette_color
    ),
    right_box_arc = list(
      geom  = "curve",
      x     = x_max - (16.5 * x_adj),
      xend  = x_max - (16.5 * x_adj),
      y     = y_mid + (ifelse(coord_flip, -1, 1) *
                         sqrt((y_adj * 5.5) ^ 2 + (y_adj * 9.15) ^ 2)),
      yend  = y_mid - (ifelse(coord_flip, -1, 1) *
                         sqrt((y_adj * 5.5) ^ 2 + (y_adj * 9.15) ^ 2)),
      color = palette_color
    ),
    lower_left_arc = list(
      geom  = "curve",
      x     = ifelse(coord_flip, x_min, x_min + 2 * x_adj),
      xend  = ifelse(coord_flip, x_min + 2 * x_adj, x_min),
      y     = ifelse(coord_flip, y_min + 2 * y_adj, y_min),
      yend  = ifelse(coord_flip, y_min, y_min + 2 * y_adj),
      color = palette_color
    ),
    upper_left_arc = list(
      geom  = "curve",
      x     = ifelse(coord_flip, x_min + 2 * x_adj, x_min),
      xend  = ifelse(coord_flip, x_min, x_min + 2 * x_adj),
      y     = ifelse(coord_flip, y_max, y_max - 2 * y_adj),
      yend  = ifelse(coord_flip, y_max -2 * y_adj, y_max),
      color = palette_color
    ),
    lower_right_arc = list(
      geom  = "curve",
      x     = ifelse(coord_flip, x_max - 2 * x_adj, x_max),
      xend  = ifelse(coord_flip, x_max, x_max - 2 * x_adj),
      y     = ifelse(coord_flip, y_min, y_min + 2 * y_adj),
      yend  = ifelse(coord_flip, y_min + 2 * y_adj, y_min),
      color = palette_color
    ),
    upper_right_arc = list(
      geom  = "curve",
      x     = ifelse(coord_flip, x_max, x_max - 2 * x_adj),
      xend  = ifelse(coord_flip, x_max - 2 * x_adj, x_max),
      y     = ifelse(coord_flip, y_max - 2 * y_adj, y_max),
      yend  = ifelse(coord_flip, y_max, y_max - 2 * y_adj),
      color = palette_color
    )
  )

  invoke_map(fcn_list, arg_list)
}
```

---

## Annotate to enhance

.tiny[
```{r fig.width=7, fig.height=4.66}
ggplot(shots, mapping = aes(x = start_x, y = start_y)) +
  fc_annotate_pitch(dimensions = c(100, 100)) +
  geom_point(mapping = aes(color = factor(team_id)), size = 3) +
  labs(color = "Team ID") +
  theme_void() +
  theme(legend.position = "bottom")
```
]

--

Much more informative! Full function: [fc_annotate_pitch()](http://www2.stat.duke.edu/~sms185/R/fc_annotate_pitch.R)

---

class: inverse, center, middle

# Organizing plots: package `patchwork`

---

class: inverse, center, middle

# Aside: parliament plots with `ggpol`

---

## Data: Congressional seats

```{r}
url <- str_c("http://www2.stat.duke.edu/~sms185/",
             "data/politics/congress_long.csv")
congress <- read_csv(url)
congress
```

---

## Parliament plot

.tiny[
```{r fig.width=8, fig.height=4}
ggplot(data = congress[congress$year_start == 1913 & congress$branch == "house", ]) +
  geom_parliament(aes(seats = seats, fill = factor(party)), show.legend = TRUE, color = "black") + #<<
  scale_fill_manual(values = c("#3A89CB", "#D65454", "#BF6FF0", "Grey"), 
                    labels = c("Dem", "GOP", "Other", "Vacant")) +
  labs(fill = "Party") +
  coord_fixed() +
  theme_void(base_size = 20)
```
]

---

## Package `ggpol`

- Package `ggpol` supports a few other `geom` functions: 

    - `geom_arcbar()`,
    - `geom_bartext()`, 
    - `geom_circle()`, 
    - `geom_tshighlight()`,
    - `geom_boxjitter()`.

- See https://github.com/erocoar/ggpol

---

## My function: `plot_congress()`

.tiny[
```{r}
plot_congress <- function(data, year, leg_branch, legend = TRUE, text_size = 8) {
  data %>% 
    filter(year_start == year, branch == leg_branch) %>% 
    ggplot() +
    geom_parliament(aes(seats = seats, fill = factor(party)), 
                    show.legend = legend, color = "black") +
    scale_fill_manual(values = c("#3A89CB", "#D65454", "#BF6FF0", "Grey"), 
                      labels = c("Dem", "GOP", "Other", "Vacant")) +
    annotate("text", x = 0, y = .5, label = paste(year, leg_branch), 
             size = text_size) +
    labs(fill = "Party") +
    coord_fixed() +
    theme_void(base_size = 20)
}
```
]

Use package `patchwork` to organize multiple plots in a single window. No need
to facet.

```{r}
my_plot <- ggplot()
class(my_plot)
```

---

## Plot creation

```{r}
ph_1993 <- plot_congress(congress, 1993, "house")

ph_2001 <- plot_congress(congress, 2001, "house", legend = FALSE)

ph_2009 <- plot_congress(congress, 2009, "house", legend = FALSE)

ph_2017 <- plot_congress(congress, 2017, "house", legend = FALSE)
```

<br/>

Object `ph_1993` has a legend, the rest do not.

---

## Horizontal patchwork

```{r fig.width=14, fig.height=8, cache=TRUE}
ph_1993 + ph_2017
```

---

## Vertical patchwork

```{r fig.width=14, fig.height=8, cache=TRUE}
ph_1993 + ph_2017 + plot_layout(ncol = 1)
```

---

## Group patchwork

```{r fig.width=16, fig.height=10, cache=TRUE}
ph_1993 + (ph_2001 + ph_2009) + ph_2017 + 
  plot_layout(ncol = 1, widths = 1)
```

---

```{r fig.width=16, fig.height=10, cache=TRUE}
(ph_1993 | ph_2001) / (ph_2009 | ph_2017)
```

---

```{r echo=FALSE}
ps_1993 <- plot_congress(congress, 1993, "senate", legend = FALSE, text_size = 6)
ps_2001 <- plot_congress(congress, 2001, "senate", legend = FALSE, text_size = 6)
ps_2009 <- plot_congress(congress, 2009, "senate", legend = TRUE, text_size = 6)
ps_2017 <- plot_congress(congress, 2017, "senate", legend = FALSE, text_size = 6)
```

```{r fig.width=12, cache=F}
(ps_1993 | ps_2001 | ps_2009) /  ps_2017 + plot_layout(widths = 1)
```

???

.tiny[
```{r}
ps_1993 <- plot_congress(congress, 1993, "senate", legend = FALSE, text_size = 6)
ps_2001 <- plot_congress(congress, 2001, "senate", legend = FALSE, text_size = 6)
ps_2009 <- plot_congress(congress, 2009, "senate", legend = TRUE, text_size = 6)
ps_2017 <- plot_congress(congress, 2017, "senate", legend = FALSE, text_size = 6)
```
]

---

## Package `patchwork`

- Supports operators `+`, `-`, `|` (besides), `/` (over)

- Specify layouts and spacing with `plot_layout()`, `plot_spacer()`, 
  respectively

- Add grouping with `{ }` or `( )`

- Use `&` or `*` to add elements to all subplots, `*` only affects current
  nesting level

- See https://github.com/thomasp85/patchwork

---

class: inverse, center, middle

# Exercise

---

## Flint water data

Create a set of visualizations based on tibble object `flint`. Use patchwork
to combine these in a single plot window.

```{r}
url <- str_c("http://www2.stat.duke.edu/~sms185/",
             "data/health/flint.csv")
flint <- read_csv(url)
flint
```

---

class: inverse, center, middle

# Animation: `gganimate()`

---

## Data: `gapminder`

```{r}
library(gapminder) 
gapminder
```

---

## Nothing new

.tiny[
```{r fig.width=12, fig.height=6}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~continent) +
  theme_bw(base_size = 16)
```
]

---

## Animate with `gganimate()`

```{r cache=TRUE, echo=FALSE, fig.width=12, fig.height=7}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~continent) +
  theme_bw(base_size = 16) +
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'Life expectancy') + #<<
  transition_time(year) + #<<
  ease_aes('linear') #<<
```

---

## What did we add?

Base plot

.tiny[
```{r eval=FALSE}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~continent) +
  theme_bw(base_size = 16)
```
]

--

Transform to animation

.tiny[
```{r eval=FALSE}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(~continent) +
  theme_bw(base_size = 16) +
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'Life expectancy') + #<<
  transition_time(year) + #<<
  ease_aes('linear') #<<
```
]

---

## Another example

First, reshape the data.

```{r}
flint_long <- flint %>% 
  pivot_longer(cols = draw1:draw3, names_to = "draw", values_to = "pb_level")
```

--

```{r}
p <- flint_long %>% 
  filter(zip == 48507, pb_level < 75) %>%
  mutate(flush_time = case_when(
    draw == "draw1" ~ 0,
    draw == "draw2" ~ 45,
    draw == "draw3" ~ 120
  )) %>% 
  ggplot(mapping = aes(x = flush_time, y = pb_level, group = id)) +
  geom_line() +
  geom_point(aes(group = seq_along(flush_time)), size = 3) +
  geom_point(color = "blue", size = 3) +
  scale_x_continuous(breaks = c(0, 45, 120), 
                     labels = c("Draw 1", "Draw 2", "Draw 3")) +
  geom_line(color = "grey90") +
  labs(y = "Lead level (ppb)", x = "") +
  theme_bw(base_size = 16)
```

---

class: center, middle

```{r echo=FALSE}
p
```

---

```{r}
p <- p + transition_reveal(flush_time)
animate(p, end_pause = 30)
```

---

## Package `gganimate`

- Core functions
    - `transition_*()` defines how the data should be spread out and how it 
      relates to itself across time.
  
    - `view_*()` defines how the positional scales should change along the 
      animation.

    - `shadow_*()` defines how data from other points in time should be presented 
      in the given point in time.

    - `enter_*()` / `exit_*()` defines how new data should appear and how old data 
      should disappear during the course of the animation.

    - `ease_aes()` defines how different aesthetics should be eased during 
      transitions.
      
- Label variables
    - function dependent, use `{` `}` to access their values.

- See https://gganimate.com

---

class: inverse, center, middle

# Interactive plots: `ggiraph`

---

## Data: NC births and SID

```{r}
nc <- read_csv("http://www2.stat.duke.edu/~sms185/data/health/nc_birth_sid.csv")
nc
```

---

## Standard scatter plot

.tiny[
```{r echo=FALSE, fig.width=10, fig.height=7}
ggplot(nc, mapping = aes(x = AREA, y = BIR74)) +
  geom_point(size = 4, alpha = .5) +
  theme_minimal()
```
]

---

## Make it interactive

- **using a `tooltip`**

```{r eval=FALSE}
gg_name <- ggplot(nc, mapping = aes(x = AREA, y = BIR74)) +
  geom_point_interactive(aes(tooltip = NAME), size = 4, alpha = .5) + #<<
  theme_minimal()

girafe(ggobj = gg_name)
```

--

- **using hover functionality**

```{r eval=FALSE}
gg_hover <- ggplot(nc, mapping = aes(x = AREA, y = BIR74)) +
  geom_point_interactive(aes(data_id = NAME, tooltip = NAME), #<<
                         size = 4, alpha = .5) +
  theme_minimal()

girafe(ggobj = gg_hover)
```

---

- **using on-click functionality**

```{r eval=FALSE}
nc$wiki <- paste0('window.open(\"', 
                  "https://www.ncpedia.org/geography/", 
                  tolower(nc$NAME), '\")')

gg_name <- ggplot(nc, mapping = aes(x = AREA, y = BIR74)) +
  geom_point_interactive(aes(tooltip = NAME, onclick = wiki), #<<
                         size = 4, alpha = .5) +
  theme_minimal()

girafe(ggobj = gg_name)
```

---

## Package `ggiraph`

- Add tooltips, animations, and JavaScript actions to ggplot graphics

- In general, instead of `geom_<plot_type>()` use
  `geom_<plot_type>_interactive()`

- Interactivity is added to ggplot geometries, legends and theme elements, 
  via the following aesthetics:
    - tooltip: tooltips to be displayed when mouse is over elements
    
    - onclick: JavaScript function to be executed when elements are clicked
    
    - data_id: id to be associated with elements (used for hover and click actions)

- Function `girafe()` translates the graphic into an interactive web-based
  graphic

- See https://github.com/davidgohel/ggiraph

---

## References

1. A Grammar of Animated Graphics. (2021). 
   https://gganimate.com/

2. Create GIFs with gifski in knitr Documents - Yihui Xie | 谢益辉. (2021).
   https://yihui.org/en/2018/08/gifski-knitr/

3. davidgohel/ggiraph. (2021).
   https://github.com/davidgohel/ggiraph

4. erocoar/ggpol. (2021). 
   https://github.com/erocoar/ggpol

5. Extending ggplot2. (2021). 
   https://ggplot2.tidyverse.org/articles/extending-ggplot2.html

6. thomasp85/patchwork. (2021).
   https://github.com/thomasp85/patchwork

7. Top 50 ggplot2 Visualizations - The Master List (With Full R Code). (2020).
   http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html



